13th International Satisfiability Modulo Theories Competition (SMT-COMP 2018): Rules and Procedures

### 2018-04-10 rules/rules18.tex
Updated dates.

@@

\title{12th International Satisfiability Modulo Theories Competition
  (SMT-COMP 2017): Rules and Procedures}

@@

\noindent Additional material will be made available at the
competition web site, \url{www.smtcomp.org} or
\url{smtcomp.sourceforge.net/2017}.

@@

SMT-COMP~2017 is part of the SMT Workshop~2017
(\url{http://smt-workshop.cs.uiowa.edu/2017/}), which is affiliated
with CAV~2017 (\url{http://cavconference.org/2017/}).  The SMT
Workshop will include a block of time to present the results of the
competition.

@@

SMT-COMP 2017 will have three tracks: the conventional main track, an
application (i.e., incremental) track, and an unsat-core track.

@@

The rest of this document, revised from the previous
version,\footnote{Earlier versions of this document include
  contributions from Clark Barrett, Roberto Bruttomesso, David Cok,
  Sylvain Conchon, David D{\'e}harbe, Morgan Deters, Alberto Griggio,
  Matthias Heizmann, Albert Oliveras, Aaron Stump, and Tjark Weber.}
describes the rules and competition procedures for SMT-COMP~2017.  The
principal changes from the previous competition rules are the
following:
\begin{itemize}
\item Submission of accompanying information for solvers is via a web
  form (rather than by email to the organizers).  \emph{Rationale:}
  Email submissions were often incomplete, leading to ambiguity and
  further inquiries.  The form provides a more structured way of
  submitting information.
\item Benchmarks will use (a subset of) version~2.6 of the SMT-LIB
  language.  \emph{Rationale:} This is the latest version of the
  SMT-LIB language.  It is largely backwards-compatible with earlier
  versions (in particular~2.0 and~2.5).
\item Benchmarks that use partial bit-vector functions, such as
  \texttt{bvudiv}, or underspecified floating-point functions, such as
  \texttt{fp.min}, will be eligible for the competition again.
  \emph{Rationale:} A conclusion on the semantics of these functions
  has finally been reached, and the status of affected SMT-LIB
  benchmarks has been updated accordingly.
\item Benchmarks with unknown status will be eligible for the
  competition's main track.  In 2016, solver performance on benchmarks
  with unknown status was evaluated but reported separately; in 2017,
  it will directly affect the competition results.  \emph{Rationale:}
  Using only benchmarks with known status (i.e., benchmarks that have
  been solved before) to determine the competition results unjustly
  favors imitation of existing solvers over true innovation.
\item In the competition-wide scoring, the (per-division) penalty for
  erroneous results is changed from the number of errors to a fixed
  constant (multiplied by the weight of the respective division).
  \emph{Rationale:} The weight already takes the number of benchmarks
  in the division into account; multiplying it by the number of errors
  overemphasizes large divisions.
\item The unsat-core track, which was re-introduced in 2016, is no
  longer experimental.  Its divisions will be considered competitive
  if the necessary requirements (see Section~\ref{sec:scoring}) are
  met.  \emph{Rationale:} Rules and tool support for the unsat-core
  track proved sufficiently stable in 2016.
\item The competition will feature experimental divisions for
  benchmarks that use algebraic datatypes.  \emph{Rationale:}
  Algebraic datatypes are specified in the draft SMT-LIB~2.6 standard,
  which is expected to become official in the near future, and are
  already supported by some solvers.  Benchmarks that use datatypes
  have recently been added to SMT-LIB.
\end{itemize}

@@

For participation in SMT-COMP, a solver must be uploaded to StarExec
and made publicly available.  StarExec supports solver configurations;
for clarity, \emph{each submitted solver must have one configuration
  only}.  Moreover, the organizers must be informed of the solver's
presence \emph{and the tracks and divisions in which it is
  participating} via the web form at
\begin{center}
  \url{https://goo.gl/forms/HL6rbOywqW4sFo1D2}
\end{center}
A submission must also include a 32-bit unsigned integer.  These
integer numbers, collected from all submissions, are used to seed the
benchmark scrambler.

@@

SMT-COMP entrants must be submitted via StarExec (solvers) \emph{and}
the above web form (accompanying information) until the end of {\bf
  June~4, 2017} anywhere on earth.  After this date no new entrants
will be accepted.  However, updates to existing entrants on StarExec
will be accepted until the end of {\bf June~19, 2017} anywhere on
earth.

@@

\header{Dates of competition.}
%
The bulk of the computation will take place during the weeks leading
up to SMT 2017.  Intermediate results will be regularly posted to the
SMT-COMP website as the competition runs.

@@

The main track competition uses a StarExec post-processor (named
``SMT-COMP 2017") to accumulate the results.

@@

\header{New benchmarks.}
%
The deadline for submission of new benchmarks is {\bf May~1, 2017}.
The organizers, in collaboration with the SMT-LIB maintainers, will be
checking and curating these until {\bf June~1, 2017}.  The SMT-LIB
maintainers intend to make a new release of the benchmark library
publicly available on or close to this date.

@@

SMT-COMP 2017 is organized under the direction of the SMT Steering
Committee. The organizing team is
%
\begin{itemize}
\setlength{\itemsep}{0pt}
\item \href{http://www.cs.man.ac.uk/~regerg/}{Giles Reger}~--
  University of Manchester, UK (co-organizer)
\item
  \href{https://swt.informatik.uni-freiburg.de/staff/heizmann}{Matthias
    Heizmann}~-- University of Freiburg, Germany (co-organizer)
\item
  \href{http://cs.stanford.edu/people/niemetz}{Aina
    Niemetz}~-- Stanford University, USA (co-organizer)
\item \href{http://user.it.uu.se/~tjawe125/}{Tjark Weber}~-- Uppsala
  University, Sweden (chair)
\end{itemize}
%
Tjark Weber is responsible for policy and procedure decisions, such as
these rules, with input from the co-organizers. He is not associated
with any group creating or submitting solvers.

>>>>

\newcommand{\rem}[1]{\textcolor{red}{[#1]}}

@@

\title{13th International Satisfiability Modulo Theories Competition
  (SMT-COMP 2018): Rules and Procedures}

@@

\noindent Additional material will be made available at the
competition web site, \url{www.smtcomp.org} or
\url{smtcomp.sourceforge.net/2018}.

@@

SMT-COMP~2018 is part of the SMT Workshop~2018
(\url{http://smt-workshop.cs.uiowa.edu/2018/}),
which is affiliated with IJCAR~2018 (\url{http://ijcar2018.org/}),
part of FLoC 2018 (\url{http://www.floc2018.org/}).
The SMT Workshop will include a block of time to present the results of the
competition.

@@

SMT-COMP 2018 will have three tracks: the conventional main track, an
application (i.e., incremental) track, and an unsat-core track.

@@

The rest of this document, revised from the previous
version,\footnote{Earlier versions of this document include
  contributions from Clark Barrett, Roberto Bruttomesso, David Cok,
  Sylvain Conchon, David D{\'e}harbe, Morgan Deters, Alberto Griggio,
  Matthias Heizmann, Albert Oliveras, Aaron Stump, and Tjark Weber.}
describes the rules and competition procedures for SMT-COMP~2018.  The
principal changes from the previous competition rules are the
following:
\begin{itemize}
\item Submission of accompanying information for solvers is via a web
  form (rather than by email to the organizers).  \emph{Rationale:}
  Email submissions were often incomplete, leading to ambiguity and
  further inquiries.  The form provides a more structured way of
  submitting information.
\item Benchmarks will use (a subset of) version~2.6 of the SMT-LIB
  language.  \emph{Rationale:} This is the latest version of the
  SMT-LIB language.  It is largely backwards-compatible with earlier
  versions (in particular~2.0 and~2.5).
\item Benchmarks that use partial bit-vector functions, such as
  \texttt{bvudiv}, or underspecified floating-point functions, such as
  \texttt{fp.min}, will be eligible for the competition again.
  \emph{Rationale:} A conclusion on the semantics of these functions
  has finally been reached, and the status of affected SMT-LIB
  benchmarks has been updated accordingly.
\item Benchmarks with unknown status will be eligible for the
  competition's main track.  In 2016, solver performance on benchmarks
  with unknown status was evaluated but reported separately; in 2017,
  it will directly affect the competition results.  \emph{Rationale:}
  Using only benchmarks with known status (i.e., benchmarks that have
  been solved before) to determine the competition results unjustly
  favors imitation of existing solvers over true innovation.
\item In the competition-wide scoring, the (per-division) penalty for
  erroneous results is changed from the number of errors to a fixed
  constant (multiplied by the weight of the respective division).
  \emph{Rationale:} The weight already takes the number of benchmarks
  in the division into account; multiplying it by the number of errors
  overemphasizes large divisions.
\item The unsat-core track, which was re-introduced in 2016, is no
  longer experimental.  Its divisions will be considered competitive
  if the necessary requirements (see Section~\ref{sec:scoring}) are
  met.  \emph{Rationale:} Rules and tool support for the unsat-core
  track proved sufficiently stable in 2016.
\item The competition will feature experimental divisions for
  benchmarks that use algebraic datatypes.  \emph{Rationale:}
  Algebraic datatypes are specified in the draft SMT-LIB~2.6 standard,
  which is expected to become official in the near future, and are
  already supported by some solvers.  Benchmarks that use datatypes
  have recently been added to SMT-LIB.
\end{itemize}

@@

For participation in SMT-COMP, a solver must be uploaded to StarExec
and made publicly available.  StarExec supports solver configurations;
for clarity, \emph{each submitted solver must have one configuration
  only}.  Moreover, the organizers must be informed of the solver's
presence \emph{and the tracks and divisions in which it is
  participating} via the web form at
\begin{center}
  \rem{TODO, this is still the old link}
  \url{https://goo.gl/forms/HL6rbOywqW4sFo1D2}
\end{center}
A submission must also include a 32-bit unsigned integer.  These
integer numbers, collected from all submissions, are used to seed the
benchmark scrambler.

@@

SMT-COMP entrants must be submitted via StarExec (solvers) \emph{and}
the above web form (accompanying information) until the end of {\bf
  May~27, 2018} anywhere on earth.
After this date no new entrants will be accepted.
However, updates to existing entrants on StarExec
will be accepted until the end of {\bf June~10, 2018} anywhere on earth.

@@

\header{Dates of competition.}
%
The bulk of the computation will take place during the weeks leading
up to SMT 2018.  Intermediate results will be regularly posted to the
SMT-COMP website as the competition runs.

@@

The main track competition uses a StarExec post-processor (named
``SMT-COMP 2018") to accumulate the results.

@@

\header{New benchmarks.}
%
The deadline for submission of new benchmarks is {\bf April~8, 2018}.
The organizers, in collaboration with the SMT-LIB maintainers, will be
checking and curating these until {\bf May~1, 2018}.  The SMT-LIB
maintainers intend to make a new release of the benchmark library
publicly available on or close to this date.

@@

SMT-COMP 2018 is organized under the direction of the SMT Steering
Committee. The organizing team is
%
\begin{itemize}
\setlength{\itemsep}{0pt}
\item
  \href{https://swt.informatik.uni-freiburg.de/staff/heizmann}{Matthias
    Heizmann}~-- University of Freiburg, Germany (co-organizer)
\item
  \href{http://cs.stanford.edu/people/niemetz}{Aina
    Niemetz}~-- Stanford University, USA (co-organizer)
\item \href{http://www.cs.man.ac.uk/~regerg/}{Giles Reger}~--
  University of Manchester, UK (co-organizer)
\item \href{http://user.it.uu.se/~tjawe125/}{Tjark Weber}~-- Uppsala
  University, Sweden (chair)
\end{itemize}
%
Tjark Weber is responsible for policy and procedure decisions, such as
these rules, with input from the co-organizers. He is not associated
with any group creating or submitting solvers.
